---
title: "Simulation for Latent Factor Splines"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Setup

```{r}
library("knitr")
read_chunk("spline_sim.R")
```

```{r, libraries}
```

## Preliminary plots

First, we can plot result of the example spline latent factor
model. There isn't that much noise in the example, so of course the
reconstruction is good.

```{r, example-reconstruction}
```

Beware overinterpreting the latent sources though! They are only
unique up to rotations.

```{r, example-sources}
```

## Simulations

A natural question is how well we can reconstruct the data, in
different noise and missigness regimes, this is simulated below. We
might have also wanted to know performance changes when the true
number of latent sources or complexity of the basis changes, but these
are omitted for now. We might also be interested in how the model
performs under various misspecifications (incorrect basis, wrong
number of sources, nongaussianity, outliers, etc.), but this is also
omitted.

In a few cases, the coordinate descent estimates blew up. Really, we
should be tuning the step-sizes according to the noise level, or at
least do a line search. So, in practice, this kind of behavior can be
avoided.

```{r, simulation-data, echo = F}
```

```{r, sim-funs}
```

```{r, process-sims}
```

The fact that it seems like the RSS is going down with higher
missingness is misleading, it should be averaged only over observed
points.

```{r, plot-sim}
```
